Notes

### 2020-02-11 notes.Rmd
Hollow sphere example added.

>>>>

The fisheye display makes it look more like a hollow sphere, so how then does a hollow sphere look like with this new display? In this case the standard projected view is still denser in the center (but less so than the full hypersphere), and the fisheye display now shows lower density in the center.

<img src="sphere6h_xy.gif" width="450"/><img src="sphere6h_fe.gif" width="450"/>
